\emph{Appendices for}\\Intergroup contact fosters\\more inclusive social identities

### 2018-10-26 manuscript/appendices.tex
update appendices

Informed by local knowledge, we intended to rely on last names to unobtrusively communicate caste membership in the crossed-categorization task. To find the most prototypical stimuli, wecompiled an initial set of 50 surnames, drawing on local knowledge, databases on naming preferences, and publicly available archives of Facebook usernames. We selected 10 surnames for each of five combinations of nationality, religion, and caste: (1) Indian Hindus of upper-caste backgrounds, (2) Indian Hindus of lower-caste backgrounds (Dalits), (3) Indian Muslims, (4) foreign Hindus, and (5) foreign Muslims. From these 50 names, we created 100 stimuli resembling identity cards, 50 with female first names and 50 with male first names. Each card had the target's first and last name, age (21--26 years), and religion (Hindu, Muslim) printed on them, as well as a flag corresponding to the target's nationality (Indian, Nepali, Sri Lankan, Bangladeshi) and a silhouette corresponding to the target's gender \cite<adapted~from>{ma_chicago_2015}. Cards for female and male targets were identical in all attributes except first name and silhouette.

@@

Participants' responses had important implications for designing the crossed-categorization task. On average, participants regarded all targets' names as at least ``somewhat typical'' $(1.42 \le \textit{Ms} \le 3.50)$. Names, however, were not enough to reliably cue caste membership---only $55\%$ to $83\%$ of participants identified even the most distinctive Dalit targets as Scheduled Caste~/ Scheduled Tribe (see Figure~\ref{fig:a-1}). Further, participants consistently categorized Muslim targets as Other Backward Class (see Figure~\ref{fig:a-2}), introducing a potential confound when comparing Muslim (OBC) and Hindu (GM) targets. Considering these findings, we decided to explicitly state caste membership (as reservation categories: GM, OBC, SC/ST) for Indian targets, and to add \emph{Indian, Hindu, OBC} targets as a sixth category.

@@

Van Dommelen et al. \citeyear{dommelen_construing_2015} analysed participants' responses as \emph{Social Identity Inclusiveness}, i.e. the total number of 24 targets a participant had categorized as ``us'', and as \emph{Social Identity Structures}, i.e. the specific structures proposed by \citeA{roccas_social_2002}. Neither measure translated well to the present study. As participants had different caste backgrounds, comparing their inclusiveness scores ($M = 15.34$, $\textit{SD} = 4.88$, $\textit{Mdn} = 16$) was less meaningful than in \citeauthor{dommelen_construing_2015}'s sample. Coding structures was interesting in principle, but proved difficult in practice.  Few (9\%, $n = 26$) participants consistently classified all targets in each category as either ``us'' or ``not us''. Relatedly, how participants classified targets within a category was correlated, but only moderately so ($.41 \leq rs \leq.66$, see Table ~\ref{tab:ch4-s4-2}). The inconsistency in participants' responses made hard and fast coding rules, as used by \citeauthor{dommelen_construing_2015}, impractical.

\begin{table}
\centering
\figureversion{lining, tabular}
\caption[Mean intra and inter-category correlations for target categorizations]{Mean \emph{intra}-category (\textbf{diagonal}) and \emph{inter}-category correlations between participants' categorizations of targets in the respective categories.}
\small	
\begin{tabular}{rlrrrr|rr} \toprule
\# & Category            & 1   & 2   & 3   & 4   & 5   & 6   \\ \midrule \addlinespace
1  & Indian, Hindu, GM   & \textbf{.48} & .56 & .33 & .43 & .16 & .08 \\
2  & Indian, Hindu, OBC  & .56 & \textbf{.41} & .29 & .46 & .09 & .06 \\
3  & Indian, Hindu, SCST & .33 & .29 & \textbf{.66} & .35 & .03 & .16 \\
4  & Indian, Muslim, OBC & .43 & .46 & .35 & \textbf{.52} & .01 & .24 \\ \midrule
5  & Foreign, Hindu      & .16 & .09 & .03 & .01 & \textbf{.50} & .47 \\
6  & Foreign, Muslim     & .08 & .06 & .16 & .24 & .47 & \textbf{.51} \\ \addlinespace \bottomrule
\end{tabular}
\label{tab:ch4-s4-2}
\end{table}

@@

We used the following analytic strategy: First, we tested for \emph{group differences} in participants' perceptions of (dis-)advantage and in their support for affirmative action. Second, we analysed to what extent contact experiences and ingroup construals explained \emph{individual differences} in participants' responses. We examined participants' responses to measures concerning outgroup members to test the \emph{solidarity hypothesis} (that positive contact encourages advantaged-group members to support social change). We examined participants' responses to measures concerning their ingroup to test the \emph{demobilisation hypothesis} (that positive contact discourages disadvantaged-group members from supporting social change) and the \emph{mobilisation hypothesis} (that negative contact encourages disadvantaged-group members to support social change).

@@

We investigated how participants' caste memberships shaped their perceptions of life difficulty and their support for reservations. To that end, we estimated two Bayesian multivariate models in \emph{RStan} \cite{rstan_package} with participants' responses to six perceived life difficulty and three policy support measures as outcome variables.\footnote{For this analysis, we aggregated items so that target groups corresponded across the two outcome measures. For perceived life difficulty, we aggregated items for Scheduled Caste and Scheduled Tribe groups, resulting in six variables. For policy support, We aggregated items for Scheduled Castes / Scheduled Tribes reservations, and for Other Backward Classes reservations, resulting in three variables.} Both models estimated how participant $j$ responded to each of the nine outcomes. Models derived the likelihood of the observed responses from a multivariate normal distribution: $$ \textbf{Y} \sim \text{MVNormal} (\mu_{jk}, \textbf{S} ) $$ where $\textbf{Y}$ is the matrix of observed variable scores (columns) across participants (rows), $\mu_{jk}$ is the estimated response to item $k$ by participant $j$, and $\textbf{S}$ is the variance-covariance matrix across variables. This means that models estimated distinct means and residual variances for each outcome, as well as residual correlations between all outcomes. Models assigned weakly informative priors to all intercepts, coefficients, and residual variances: 
\begin{align*} 
\beta & \sim \text{Normal} (0, 1) \\ 
\sigma & \sim \text{Cauchy} (0, 1)
\end{align*}
allowing a wide range of plausible effect sizes. Model~0 estimated distinct means for each outcome, but did not consider participants' group memberships: $ \mu_{jk} =  \beta_k $, where $\mu_{jk}$ equals $\beta_{k}$, the fixed intercept for outcome $k$. Model~1 estimated distinct means across participants' ingroups: $ \mu_{jk} =  \beta_k + \beta_{k,\text{OBC}} + \beta_{k,\text{SCST}} $, where $\mu_{jk}$ equals $\beta_k$, the fixed intercept for outcome $k$, plus $\beta_{k,\text{OBC}}$ and $\beta_{k,\text{SCST}}$, the coefficients estimating by how much Other Backward Class and Scheduled Caste~/ Scheduled Tribe participants' responses differed from General Merit participants'. Model~1 made better out-of-sample predictions than Model~0, $\Delta\textit{ELPD} = 94.7$, $SE = 14.1$, $\frac{\Delta\textit{ELPD}}{\textit{SE}} = 6.7$. This comparison shows that participants' caste memberships shaped their perceived discrimination and policy support ratings.

Figure \ref{fig:ch5-s4-1} shows estimated mean ratings of perceived life difficulty for all target groups as a function of participants' caste memberships in Model~1. For most target groups, General Merit and Other Backward Class participants' responses closely resembled each other. On average, General Merit~/ Other Backward Class participants thought that it was somewhat hard (below the midpoint) for ``people from [their] own background'' to succeed. General Merit~/ Other Backward Class participants agreed with each other that it was a lot easier for people from Scheduled Caste~/ Scheduled Tribe backgrounds to succeed, compared to people from their own background. General Merit~/ Other Backward Class participants also agreed that, of all target groups, life was most difficult for people from General Merit backgrounds. Other Backward Class participants disagreed with General Merit participants when rating life difficulty for people from Other Backward Class backgrounds. General Merit participants rated life difficulty for Other Backward Class people as somewhat easy, while Other Backward Class participants tended toward ``neither easy nor hard'' and ``somewhat hard''. Scheduled Caste~/ Scheduled Tribe participants' responses differed markedly from General Merit and Other Backward Class participants'. For all target groups, Scheduled Caste~/ Scheduled Tribe participants rated life difficulty as ``neither easy nor hard'', on average. General Merit, Other Backward Class, and Scheduled Caste~/ Scheduled Tribe participants all tended to rate life difficulty for Muslims as around the midpoint. Overall, participants' responses seemed to contradict, or even reverse, persisting social inequalities (see Chapter~4, \emph{Caste, religion, and nation in South India}).

\begin{figure}
\centering
\includegraphics[scale=1]{../figures/figure-7}
\caption{
Posterior probabilities of perceived (dis-)advantage ratings for different target groups (right) by participants' caste ingroup (left). Diamonds mark the most plausible estimate of each mean rating; intervals encompass the 97\% most plausible estimates. GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
}
\label{fig:ch5-s4-1}
\end{figure}

Figure \ref{fig:ch5-s4-2} shows estimated policy support---that is, support for reservations benefiting Scheduled Caste~/ Scheduled Tribe, Other Backward Class, and Muslim students---as a function of participants' caste memberships in Model~1. General Merit and Other Backward Class participants' responses did not provide evidence for cross-group solidarity. General Merit participants tended to oppose reservations for Scheduled Caste~/ Scheduled Tribe ($M = 1.87$, $[1.63, 2.12]$), Other Backward Class ($M = 2.70$, $[2.44, 2.96]$), and Muslim students ($M = 2.75$, $[2.46, 3.01]$). Other Backward Class participants tended to support reservations for their own group ($M = 3.72$, $[3.50, 3.95]$), but not for Scheduled Caste~/ Scheduled Tribe ($M = 2.31$, $[2.10, 2.53]$) or Muslim ($M = 2.79$, $[2.55, 3.04]$) students. Scheduled Caste~/ Scheduled Tribe participants tended to support reservations for their own group ($M = 4.16$, $[3.88, 4.45]$), for Other Backward Class students ($M = 3.57$, $[3.27, 3.86]$), and, to a lesser extent, for Muslim students ($M = 3.24$, $[2.92, 3.57]$). Overall, participants' responses provided evidence for solidarity from Scheduled Caste~/ Scheduled Tribe participants to Other Backward Class students, but not for solidarity from General Merit and Other Backward Class participants to Scheduled Caste~/ Scheduled Tribe students.

\begin{figure}
\centering
\includegraphics[scale=1]{../figures/figure-8}
\caption{
Posterior probabilities of policy support ratings for different target groups (right) by participants' caste ingroup (left). Diamonds mark the most plausible estimate of each mean rating; intervals encompass the 97\% most plausible estimates. GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
}
\label{fig:ch5-s4-2}
\end{figure}

\begin{table}
\centering
\figureversion{lining, tabular}
\caption[Estimated residual correlations in Models 0 and 1 for Study 4]{Estimated residual correlations between six \emph{perceived life difficulty} (PD) ratings and three \emph{policy support} (PS) ratings in Model~0 (below the diagonal) and Model~1 (above the diagonal) for Study 4.}
\small	
\begin{tabularx}{\linewidth}{rl@{~}Xrrrrrr|rrr} \toprule
\# & \multicolumn{2}{l}{Variable} & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\ \midrule \addlinespace
1 & PD, & \ldots own background & \textbf{}  & .14 & .30 & .45 & .43 & .05 & .28 & .12 & .14 \\
2 & PD, & SC/ST  & .10 & \textbf{} & .33 & -.13 & -.09 & .28 & -.12 & -.10 & -.05 \\
3 & PD, & OBC    & .28 & .33 & \textbf{} & .20 & .16 & .32 & .05 & -.17 & -.13  \\
4 & PD, & GM     & .47 & -.18 & .18 & \textbf{} & .61 & -.08 & .24 & .15 & .02 \\
5 & PD, & Hindu  & .44 & -.12 & .15 & .62 & \textbf{} & -.01 & .29 & .11 & .03  \\
6 & PD, & Muslim & .04 & .28 & .31 & -.10 & -.02 & \textbf{} & .02 & -.17 & -.15 \\ \midrule
7 & PS, & SC/ST  & .29 & -.24 & -.03 & .33 & .30 & -.03 & \textbf{} & .24 & .34 \\
8 & PS, & OBC    & .11 & -.13 & -.25 & .17 & .12 & -.16 & .28 & \textbf{} & .47 \\
9 & PS, & Muslim & .16 & -.09 & -.13 & .06 & .05 & -.16 & .36 & .45 & \textbf{}   \\ \addlinespace \bottomrule
\end{tabularx}
\label{tab:ch5-s4-1}
\end{table}

Table~\ref{tab:ch5-s4-1} shows the estimated residual correlations before (Model~0) and after (Model~1) accounting for group differences. Perceiving a group to be disadvantaged correlated weakly with more support for reservations benefiting Scheduled Caste~/ Scheduled Tribe ($r = -.12 $, $[-.24,.01]$), Other Backward Class ($r = -.17$, $[-.30,-.05]$), and Muslim ($r = -.15$, $[-.28,-.03]$) students in Model~1. Support for reservations for one target group correlated moderately with support for reservations for the other target groups, $.24 < r < .47$. These correlations provided evidence for systematic variation in policy support ratings across participants, even after accounting for group differences. In the next section, we examine to what extent contact experiences and ingroup construals explain this variation across individuals.

@@

We examined to what extent contact experiences and ingroup construals (measured as participants' responses in the crossed-categorization task) accounted for individual differences in perceived life difficulty and policy support. To that end, we estimated a series of Bayesian multilevel models with either perceived life difficulty or policy support as outcome variable. Models derived the likelihood of the observed responses from a normal distribution: $$ y_{ij} \sim \text{Normal} (\mu_{ij}, \sigma) $$ where $y_{ij}$ is the observed response to item $i$ by participant $j$, and $\mu_{ij}$ is the estimated response to item $i$ by participant $j$, $\sigma$ is the estimated residual variance (expressed as standard deviation). We used the same weakly informative priors as for the multivariate models.

First, we estimated participants' responses to each of five perceived life difficulty items, with General Caste (GM), Scheduled Caste (SC), Scheduled Tribe (ST), Other Backward Class (OBC), and Muslims as target groups. Model~0 estimated item responses as varying across participants and target groups, and estimated differences across participants' ingroups: $$ \mu_{ij} = \beta_{j} + \beta_{kl} $$ where $\mu_{ij}$, the estimated mean response to item $i$ by participant $j$, equals $\beta_j$, the varying intercept for participant $j$, and $\beta_{kl}$, the varying intercept for target group~$k$ ($1 = \text{GM}$, $2 = \text{OBC}$, $3 = \text{SC/ST}$, $4 = \text{Muslims}$) and ingroup~$l$ ($1 = \text{GM}$, $2 = \text{OBC}$, $2 = \text{SC/ST}$). Model~0 thus resembled the multivariate model estimated above.

Model~1 extended Model~0 by estimating to what extent outgroup friendship and negative contact with outgroup members were associated with perceptions of life difficulty for outgroups: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \beta_\text{OF}x_{\text{OG},k}x_\text{OF,jk} + \beta_\text{NC}x_{\text{OG},jk}x_\text{OF,jk}$$ where $x_{\text{OG},jk}$ codes whether target group $k$ is an outgroup [1] or ingroup [0] for participant $j$, $x_\text{OF,jk}$ and $x_\text{NC,jk}$ are, respectively, participant $j$'s outgroup friendship and negative contact with target group $k$, and $\beta_\text{OF}$ and $\beta_\text{NC}$ estimate the increase in participants' ratings for each additional standard deviation of reported contact. Model~2 estimated the effects of outgroup friendship and negative contact on outgroup ratings as varying across target outgroups: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \beta_{\text{OF},k}x_{\text{OG},k}x_\text{OF,jk} + \beta_{\text{NC},k}x_{\text{OG},jk}x_\text{OF,jk}$$ where $\beta_{\text{OF},k}$ and $\beta_{\text{NC},k}$ estimate effects of contact on ratings for outgroup $k$. Neither Model~1 nor Model~2 improved upon the out-of-sample predictions of Model~0, showing that intergroup contact neither increased nor decreased participants' perceptions of discrimination against ethnoreligious or caste outgroups (see Table~\ref{tab:ch5-s4-2}).

Models~3 and 4 tested whether participants' ingroup construals were associated with their perceptions of life difficulty for various outgroups. Model~3 estimated this relationship as constant across target groups: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \beta_\text{Q1}x_{\text{OG},k}x_\text{Q1,jk} $$ where $x_{Q1,jk}$ is the proportion [0--1] of targets belonging to outgroup $k$ that participant $j$ categorized as ``us'', and $\beta_{Q1}$ estimates the difference in perceived life difficulty between participants who categorized all four targets of an outgroup as ``us'' and participants who categorized all targets of an outgroup as ``not us''. Model~4 estimated this relationship as varying across outgroups: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \beta_\text{Q1,k}x_{\text{OG},k}x_\text{Q1,jk} $$ where $\beta_{Q1,k}$ estimates the difference in perceived perceived life difficulty between participants who categorized all four targets of outgroup $k$ as ``us'' and participants who categorized all targets of outgroup $k$ as ``not us''. Neither Model~3 nor Model~4 improved upon the out-of-sample predictions of Model~0, showing that more inclusive identities neither increased nor decreased participants' perceptions of life difficulty for ethnoreligious an caste outgroups. % Overall, Models~1 to 4 did not provide evidence for the solidarity hypothesis or, more specifically, for the solidarity-by-inclusion hypothesis.

>>>>

Informed by local knowledge, we intended to rely on last names to unobtrusively communicate caste membership in the triple crossed-categorization task. To find the most prototypical stimuli, we compiled an initial set of 50 surnames, drawing on local knowledge, databases on naming preferences, and publicly available archives of Facebook usernames. We selected 10 surnames for each of five combinations of nationality, religion, and caste: (1) Indian Hindus of upper-caste backgrounds, (2) Indian Hindus of lower-caste backgrounds (Dalits), (3) Indian Muslims, (4) foreign Hindus, and (5) foreign Muslims. From these 50 names, we created 100 stimuli resembling identity cards, 50 with female first names and 50 with male first names. Each card had the target's first and last name, age (21--26 years), and religion (Hindu, Muslim) printed on them, as well as a flag corresponding to the target's nationality (Indian, Nepali, Sri Lankan, Bangladeshi) and a silhouette corresponding to the target's gender \cite<adapted~from>{ma_chicago_2015}. Cards for female and male targets were identical in all attributes except first name and silhouette.

@@

Participants' responses had important implications for designing the triple crossed-categorization task. On average, participants regarded all targets' names as at least ``somewhat typical'' $(1.42 \le \textit{Ms} \le 3.50)$. Names, however, were not enough to reliably cue caste membership---only $55\%$ to $83\%$ of participants identified even the most distinctive Dalit targets as Scheduled Caste~/ Scheduled Tribe (see Figure~\ref{fig:a-1}). Further, participants consistently categorized Muslim targets as Other Backward Class (see Figure~\ref{fig:a-2}), introducing a potential confound when comparing Muslim (OBC) and Hindu (GM) targets. Considering these findings, we decided to explicitly state caste membership (as reservation categories: GM, OBC, SC/ST) for Indian targets, and to add \emph{Indian, Hindu, OBC} targets as a sixth category.

@@

Van Dommelen et al. \citeyear{dommelen_construing_2015} analysed participants' responses as \emph{Social Identity Inclusiveness}, i.e. the total number of 24 targets a participant had categorized as ``us'', and as \emph{Social Identity Structures}, i.e. the specific structures proposed by \citeA{roccas_social_2002}. Neither measure translated well to the present study. As participants had different caste backgrounds, comparing their inclusiveness scores ($M = 15.34$, $\textit{SD} = 4.88$, $\textit{Mdn} = 16$) was less meaningful than in \citeauthor{dommelen_construing_2015}'s sample. Coding structures was interesting in principle, but proved difficult in practice.  Few (9\%, $n = 26$) participants consistently classified all targets in each category as either ``us'' or ``not us''. Relatedly, how participants classified targets within a category was correlated, but only moderately so ($.41 \leq rs \leq.66$, see Table ~\ref{tab:b-1}). The inconsistency in participants' responses made hard and fast coding rules, as used by \citeauthor{dommelen_construing_2015}, impractical.

\begin{table}
\centering
\figureversion{lining, tabular}
\caption[Mean intra and inter-category correlations for target categorizations]{Mean \emph{intra}-category (\textbf{diagonal}) and \emph{inter}-category correlations between participants' categorizations of targets in the respective categories.}
\small	
\begin{tabular}{rlrrrr|rr} \toprule
\# & Category            & 1   & 2   & 3   & 4   & 5   & 6   \\ \midrule \addlinespace
1  & Indian, Hindu, GM   & \textbf{.48} & .56 & .33 & .43 & .16 & .08 \\
2  & Indian, Hindu, OBC  & .56 & \textbf{.41} & .29 & .46 & .09 & .06 \\
3  & Indian, Hindu, SCST & .33 & .29 & \textbf{.66} & .35 & .03 & .16 \\
4  & Indian, Muslim, OBC & .43 & .46 & .35 & \textbf{.52} & .01 & .24 \\ \midrule
5  & Foreign, Hindu      & .16 & .09 & .03 & .01 & \textbf{.50} & .47 \\
6  & Foreign, Muslim     & .08 & .06 & .16 & .24 & .47 & \textbf{.51} \\ \addlinespace \bottomrule
\end{tabular}
\label{tab:b-1}
\end{table}

@@

We tested whether more inclusive identities increase support for affirmative action among advantaged-group members, but decrease support for these policies among disadvantaged-group members. First, we tested for \emph{group differences} in participants' perceptions of (dis-)advantages and in their support for affirmative action. Second, we analysed to what extent contact experiences and ingroup construals explained \emph{individual differences} in participants' responses. We examined participants' responses to measures concerning outgroup members to test the \emph{solidarity hypothesis} (that positive contact encourages advantaged-group members to support social change). We examined participants' responses to measures concerning their ingroup to test the \emph{demobilisation hypothesis} (that positive contact discourages disadvantaged-group members from supporting social change) and the \emph{mobilisation hypothesis} (that negative contact encourages disadvantaged-group members to support social change).

@@

We investigated how participants' caste memberships shaped their perceptions of (dis-)advantages and their support for reservations. To that end, we estimated two Bayesian multivariate models in \emph{RStan} \cite{rstan_package} with participants' responses to six perceived (dis-)advantage and three policy support measures as outcome variables.\footnote{For this analysis, we aggregated items so that target groups corresponded across the two outcome measures. For perceived (dis-)advantage, we aggregated items for Scheduled Caste and Scheduled Tribe groups, resulting in six variables. For policy support, We aggregated items for Scheduled Castes / Scheduled Tribes reservations, and for Other Backward Classes reservations, resulting in three variables.} Both models estimated how participant $j$ responded to each of the nine outcomes. Models derived the likelihood of the observed responses from a multivariate normal distribution: $$ \textbf{Y} \sim \text{MVNormal} (\mu_{jk}, \textbf{S} ) $$ where $\textbf{Y}$ is the matrix of observed variable scores (columns) across participants (rows), $\mu_{jk}$ is the estimated response to item $k$ by participant $j$, and $\textbf{S}$ is the variance-covariance matrix across variables. This means that models estimated distinct means and residual variances for each outcome, as well as residual correlations between all outcomes. Models assigned weakly informative priors to all intercepts, coefficients, and residual variances: 
\begin{align*} 
\beta & \sim \text{Normal} (0, 1) \\ 
\sigma & \sim \text{Cauchy} (0, 1)
\end{align*}
allowing a wide range of plausible effect sizes. Model~0 estimated distinct means for each outcome, but did not consider participants' group memberships: $ \mu_{jk} =  \beta_k $, where $\mu_{jk}$ equals $\beta_{k}$, the fixed intercept for outcome $k$. Model~1 estimated distinct means across participants' ingroups: $ \mu_{jk} =  \beta_k + \beta_{k,\text{OBC}} + \beta_{k,\text{SCST}} $, where $\mu_{jk}$ equals $\beta_k$, the fixed intercept for outcome $k$, plus $\beta_{k,\text{OBC}}$ and $\beta_{k,\text{SCST}}$, the coefficients estimating by how much Other Backward Class and Scheduled Caste~/ Scheduled Tribe participants' responses differed from General Merit participants'. Model~1 made better out-of-sample predictions than Model~0, $\Delta\textit{ELPD} = 94.7$, $SE = 14.1$, $\frac{\Delta\textit{ELPD}}{\textit{SE}} = 6.7$. This comparison shows that participants' caste memberships shaped their perceived (dis-)advantage and policy support ratings.

Figure \ref{fig:d-1} shows estimated mean ratings of perceived (dis-)advantage for all target groups as a function of participants' caste memberships in Model~1. For most target groups, General Merit and Other Backward Class participants' responses closely resembled each other. On average, General Merit~/ Other Backward Class participants thought that it was somewhat hard (below the midpoint) for ``people from [their] own background'' to succeed. General Merit~/ Other Backward Class participants agreed with each other that it was a lot easier for people from Scheduled Caste~/ Scheduled Tribe backgrounds to succeed, compared to people from their own background. General Merit~/ Other Backward Class participants also agreed that, of all target groups, life was most difficult for people from General Merit backgrounds. Other Backward Class participants disagreed with General Merit participants when rating life difficulty for people from Other Backward Class backgrounds. General Merit participants rated life difficulty for Other Backward Class people as somewhat easy, while Other Backward Class participants tended toward ``neither easy nor hard'' and ``somewhat hard''. Scheduled Caste~/ Scheduled Tribe participants' responses differed markedly from General Merit and Other Backward Class participants'. For all target groups, Scheduled Caste~/ Scheduled Tribe participants rated life difficulty as ``neither easy nor hard'', on average. General Merit, Other Backward Class, and Scheduled Caste~/ Scheduled Tribe participants all tended to rate life difficulty for Muslims as around the midpoint. Overall, participants' responses seemed to contradict, or even reverse, persisting social inequalities.

\begin{figure}
\centering
\includegraphics[scale=1]{../figures/figure-7}
\caption{
Posterior probabilities of perceived (dis-)advantage ratings for different target groups (right) by participants' caste ingroup (left). Diamonds mark the most plausible estimate of each mean rating; intervals encompass the 97\% most plausible estimates. GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
}
\label{fig:d-1}
\end{figure}

Figure \ref{fig:d-2} shows estimated policy support---that is, support for reservations benefiting Scheduled Caste~/ Scheduled Tribe, Other Backward Class, and Muslim students---as a function of participants' caste memberships in Model~1. General Merit and Other Backward Class participants' responses did not provide evidence for cross-group solidarity. General Merit participants tended to oppose reservations for Scheduled Caste~/ Scheduled Tribe ($M = 1.87$, $[1.63, 2.12]$), Other Backward Class ($M = 2.70$, $[2.44, 2.96]$), and Muslim students ($M = 2.75$, $[2.46, 3.01]$). Other Backward Class participants tended to support reservations for their own group ($M = 3.72$, $[3.50, 3.95]$), but not for Scheduled Caste~/ Scheduled Tribe ($M = 2.31$, $[2.10, 2.53]$) or Muslim ($M = 2.79$, $[2.55, 3.04]$) students. Scheduled Caste~/ Scheduled Tribe participants tended to support reservations for their own group ($M = 4.16$, $[3.88, 4.45]$), for Other Backward Class students ($M = 3.57$, $[3.27, 3.86]$), and, to a lesser extent, for Muslim students ($M = 3.24$, $[2.92, 3.57]$). Overall, participants' responses provided evidence for solidarity from Scheduled Caste~/ Scheduled Tribe participants to Other Backward Class students, but not for solidarity from General Merit and Other Backward Class participants to Scheduled Caste~/ Scheduled Tribe students.

\begin{figure}
\centering
\includegraphics[scale=1]{../figures/figure-8}
\caption{
Posterior probabilities of policy support ratings for different target groups (right) by participants' caste ingroup (left). Diamonds mark the most plausible estimate of each mean rating; intervals encompass the 97\% most plausible estimates. GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
}
\label{fig:d-2}
\end{figure}

\begin{table}
\centering
\figureversion{lining, tabular}
\caption[Estimated residual correlations in Models 0 and 1 for Study 4]{Estimated residual correlations between six \emph{perceived life difficulty} (PD) ratings and three \emph{policy support} (PS) ratings in Model~0 (below the diagonal) and Model~1 (above the diagonal) for Study 4.}
\small	
\begin{tabularx}{\linewidth}{rl@{~}Xrrrrrr|rrr} \toprule
\# & \multicolumn{2}{l}{Variable} & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\ \midrule \addlinespace
1 & PD, & \ldots own background & \textbf{}  & .14 & .30 & .45 & .43 & .05 & .28 & .12 & .14 \\
2 & PD, & SC/ST  & .10 & \textbf{} & .33 & -.13 & -.09 & .28 & -.12 & -.10 & -.05 \\
3 & PD, & OBC    & .28 & .33 & \textbf{} & .20 & .16 & .32 & .05 & -.17 & -.13  \\
4 & PD, & GM     & .47 & -.18 & .18 & \textbf{} & .61 & -.08 & .24 & .15 & .02 \\
5 & PD, & Hindu  & .44 & -.12 & .15 & .62 & \textbf{} & -.01 & .29 & .11 & .03  \\
6 & PD, & Muslim & .04 & .28 & .31 & -.10 & -.02 & \textbf{} & .02 & -.17 & -.15 \\ \midrule
7 & PS, & SC/ST  & .29 & -.24 & -.03 & .33 & .30 & -.03 & \textbf{} & .24 & .34 \\
8 & PS, & OBC    & .11 & -.13 & -.25 & .17 & .12 & -.16 & .28 & \textbf{} & .47 \\
9 & PS, & Muslim & .16 & -.09 & -.13 & .06 & .05 & -.16 & .36 & .45 & \textbf{}   \\ \addlinespace \bottomrule
\end{tabularx}
\label{tab:d-1}
\end{table}

Table~\ref{tab:d-1} shows the estimated residual correlations before (Model~0) and after (Model~1) accounting for group differences. Perceiving a group to be disadvantaged correlated weakly with more support for reservations benefiting Scheduled Caste~/ Scheduled Tribe ($r = -.12 $, $[-.24,.01]$), Other Backward Class ($r = -.17$, $[-.30,-.05]$), and Muslim ($r = -.15$, $[-.28,-.03]$) students in Model~1. Support for reservations for one target group correlated moderately with support for reservations for the other target groups, $.24 < r < .47$. These correlations provided evidence for systematic variation in policy support ratings across participants, even after accounting for group differences. In the next section, we examine to what extent contact experiences and ingroup construals explain this variation across individuals.

@@

We examined to what extent contact experiences and ingroup construals (measured as participants' responses in the triple crossed-categorization task) accounted for individual differences in perceived (dis-)advantage and policy support. To that end, we estimated a series of Bayesian multilevel models with either perceived (dis-)advantage or policy support as outcome variable. Models derived the likelihood of the observed responses from a normal distribution: $$ y_{ij} \sim \text{Normal} (\mu_{ij}, \sigma) $$ where $y_{ij}$ is the observed response to item $i$ by participant $j$, and $\mu_{ij}$ is the estimated response to item $i$ by participant $j$, $\sigma$ is the estimated residual variance (expressed as standard deviation). We used the same weakly informative priors as for the multivariate models.

First, we estimated participants' responses to each of five perceived (dis-)advantage items, with General Caste (GM), Scheduled Caste (SC), Scheduled Tribe (ST), Other Backward Class (OBC), and Muslims as target groups. Model~0 estimated item responses as varying across participants and target groups, and estimated differences across participants' ingroups: $$ \mu_{ij} = \beta_{j} + \beta_{kl} $$ where $\mu_{ij}$, the estimated mean response to item $i$ by participant $j$, equals $\beta_j$, the varying intercept for participant $j$, and $\beta_{kl}$, the varying intercept for target group~$k$ ($1 = \text{GM}$, $2 = \text{OBC}$, $3 = \text{SC/ST}$, $4 = \text{Muslims}$) and ingroup~$l$ ($1 = \text{GM}$, $2 = \text{OBC}$, $2 = \text{SC/ST}$). Model~0 thus resembled the multivariate model estimated above.

Model~1 extended Model~0 by estimating to what extent outgroup friendship and negative contact with outgroup members were associated with perceptions of (dis-)advantages for outgroups: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \beta_\text{OF}x_{\text{OG},k}x_\text{OF,jk} + \beta_\text{NC}x_{\text{OG},jk}x_\text{OF,jk}$$ where $x_{\text{OG},jk}$ codes whether target group $k$ is an outgroup [1] or ingroup [0] for participant $j$, $x_\text{OF,jk}$ and $x_\text{NC,jk}$ are, respectively, participant $j$'s outgroup friendship and negative contact with target group $k$, and $\beta_\text{OF}$ and $\beta_\text{NC}$ estimate the increase in participants' ratings for each additional standard deviation of reported contact. Model~2 estimated the effects of outgroup friendship and negative contact on outgroup ratings as varying across target outgroups: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \beta_{\text{OF},k}x_{\text{OG},k}x_\text{OF,jk} + \beta_{\text{NC},k}x_{\text{OG},jk}x_\text{OF,jk}$$ where $\beta_{\text{OF},k}$ and $\beta_{\text{NC},k}$ estimate effects of contact on ratings for outgroup $k$. Neither Model~1 nor Model~2 improved upon the out-of-sample predictions of Model~0, showing that intergroup contact neither increased nor decreased participants' perceptions of discrimination against ethnoreligious or caste outgroups (see Table~\ref{tab:d-2}).

Models~3 and 4 tested whether participants' ingroup construals were associated with their perceptions of (dis-)advantages for various outgroups. Model~3 estimated this relationship as constant across target groups: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \beta_\text{Q1}x_{\text{OG},k}x_\text{Q1,jk} $$ where $x_{Q1,jk}$ is the proportion [0--1] of targets belonging to outgroup $k$ that participant $j$ categorized as ``us'', and $\beta_{Q1}$ estimates the difference in perceived (dis-)advantage between participants who categorized all four targets of an outgroup as ``us'' and participants who categorized all targets of an outgroup as ``not us''. Model~4 estimated this relationship as varying across outgroups: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \beta_\text{Q1,k}x_{\text{OG},k}x_\text{Q1,jk} $$ where $\beta_{Q1,k}$ estimates the difference in perceived perceived life difficulty between participants who categorized all four targets of outgroup $k$ as ``us'' and participants who categorized all targets of outgroup $k$ as ``not us''. Neither Model~3 nor Model~4 improved upon the out-of-sample predictions of Model~0, showing that more inclusive identities neither increased nor decreased participants' perceptions of (dis-)advantages for ethnoreligious an caste outgroups. % Overall, Models~1 to 4 did not provide evidence for the solidarity hypothesis or, more specifically, for the solidarity-by-inclusion hypothesis.
